\ripple: Differentiable Waveforms for Gravitational Wave Data Analysis

### 2022-11-21 src/tex/ms.tex
Added table to section 3

% \usepackage[dvipsnames]{xcolor}
% \usepackage[colorlinks]{hyperref}
% \usepackage{colortbl}
\definecolor{pyBlue}{RGB}{31, 119, 180}
\definecolor{pyRed}{RGB}{214, 39, 40}
\definecolor{pyGreen}{RGB}{44, 160, 44}

@@

\subsection{Fitting Waveform Coefficients}
\label{subsec:hmc}

@@

\subsection{Fisher Forecasting}
\label{subsec:hmc}

@@

>>>>

% \usepackage[dvipsnames]{xcolor}
% \usepackage[colorlinks]{hyperref}
% \usepackage{colortbl}
\usepackage{multirow}
\definecolor{pyBlue}{RGB}{31, 119, 180}
\definecolor{pyRed}{RGB}{214, 39, 40}
\definecolor{pyGreen}{RGB}{44, 160, 44}

@@

\subsection{Fitting Waveform Coefficients}
\label{subsec:coeffs}

@@

\subsection{Fisher Forecasting}
\label{subsec:fisher}

@@

% \begin{table*}[ht!]
%     \begin{center}
%     \begin{tabular}{c|c|c|c|c|c|c|c|c}
%     \hline\hline
%     \hfil $\boldsymbol{m_1, m_2}$ &
%     \hfil $\boldsymbol{\chi_1, \chi_2}$ &
%     \hfil $\boldsymbol{D}$ &
%     \hfil $\boldsymbol{t_c}$ &
%     \hfil $\boldsymbol{\phi_c}$ &
%     \hfil $\boldsymbol{\iota}$ &
%     \hfil $\boldsymbol{\psi}$ &
%     \hfil $\boldsymbol{RA}$ &
%     \hfil $\boldsymbol{DEC}$
%     \\
%     \hline\hline
%     \hfil [0.1, 3] &
%     \hfil [0, 1] &
%     \hfil [0, 1] &
%     \hfil [0.7, 1.3] &
%     \hfil [-3, 0] &
%     \hfil [0, 3] &
%     \hfil [-3, 3] &
%     \hfil [-3, 3] &
%     \hfil [-3, 3]
%     \\
%     \hline\hline
%     \end{tabular}
%     \end{center}
%     \caption{caption here}
%     \label{tab:priors}
% \end{table*}

\begin{table}[t!]
    % \begin{center}
    \centering
    \begin{tabular}{c|c}
    \hline\hline
    $m_1, m_2$ & $\boldsymbol{U}[1.0, 50]\, \mathrm{M}_\odot$ \\ \hline
    $\chi_1, \chi_2$ & [-0.99, 0.99] \\ \hline
    $D$ & [500, 1000]\, Mpc \\ \hline
    $t_c$ & 0.0 \\ \hline
    $\phi_c$ & 0.0 \\ \hline
    Inclincation Angle, $\iota$ & $\boldsymbol{U}[0, 1]$ \\ \hline
    Polarization Angle, $\psi$ & $\boldsymbol{U}[0, 1]$ \\ \hline
    Right Ascension, $\delta$ & $\boldsymbol{U}[0, 1]$ \\ \hline
    Declination, $\alpha$ & $\boldsymbol{U}[0, 1]$ \\ 
    \hline\hline
    \end{tabular}
    % \end{center}
    \caption{Priors for the 11 dimensional parameter space used for the Fisher forecasting population analysis in Sec.~\ref{subsec:fisher}. 
    $\boldsymbol{U}$ indicates a uniform distribution between the two variables in the brackets.}
    \label{tab:priors}
\end{table}
